Hydras \& Co.

### 2022-02-19 doc/gaia-chapter.tex
making gaia's T1 an instance of ON (doc)
extension of T1add and T1mul to type E0
add a new lemma to GCanon.v

@@

\inputsnippets{T1Bridge/E0Def}
\inputsnippets{T1Bridge/E0EqP}

@@

@@

@@

>>>>

\inputsnippets{T1Bridge/refines1R, T1Bridge/refines2R}

@@

\inputsnippets{T1Bridge/E0Def}
\inputsnippets{T1Bridge/E0plusMultDef}

\inputsnippets{T1Bridge/E0EqP}

@@

\subsection{E0 as an ordinal notation}
The module \href{../theories/html/gaia.T1Bridge.html}{gaia.T1Bridge} defines an instance of class \texttt{ON E0lt compare}
(see Chapter~\ref{chap:ON}).

\inputsnippets{T1Bridge/T1compareDef}
\inputsnippets{ T1Bridge/T1compareCorrect}
\inputsnippets{T1Bridge/E0compare}
\inputsnippets{T1Bridge/E0Sto}
\inputsnippets{T1Bridge/gEpsilon0}

\inputsnippets{T1Bridge/ExampleComp}

@@

\begin{todo}
Give equations for \texttt{canon} (corresponding to the structural recursive definition in \HydrasLib.
\end{todo}

@@

\begin{todo}
  Give equations for \texttt{F\_} (corresponding to the equation
  in \HydrasLib.
\end{todo}
